Depletion capabilities in the OpenMC Monte Carlo particle transport code

### 2020-06-24 manuscript.tex
Move figures

\Cref{fig:pwr-actinides-full} shows the relative difference in predicted
actinide concentrations between OpenMC and Serpent at four different burnup
values. The fission products that are shown in \cref{fig:pwr-actinides-full}
have been chosen because they are either strong neutron absorbers or significant
contributors to decay heat and/or radiotoxicity. We see that most of the
differences are less than 0.1\%, and all are within 0.15\%. The differences in
$^{235}$U and $^{239}$Pu concentrations increase slightly with increasing
burnup, which most likely accounts for the 20 pcm difference observed for the
full chain in \cref{fig:pwr-keff}. While not shown, the predicted actinide
concentrations for the reduced chain are nearly identical to those observed for
the full chain in \cref{fig:pwr-actinides-full}. \Cref{fig:pwr-actinides-casl}
shows the differences in actinide concentrations using the CASL depletion chain.
Because the CASL depletion chain differs from the full depletion chain primarily
with respect to how fission products are treated, the differences reported in
\cref{fig:pwr-actinides-casl} closely mirror those in
\cref{fig:pwr-actinides-full}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_actinides_full.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the full
  depletion chain.}
  \label{fig:pwr-actinides-full}
\end{figure}
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_actinides_casl.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the CASL
  depletion chain.}
  \label{fig:pwr-actinides-casl}
\end{figure}

The predicted concentration of fission products depends on both the depletion
chain that is used and the method for handling the energy dependence of the FPY.
We begin with results for the full depletion chain and interpolated FPYs, which
most closely matches the method used in Serpent; \cref{fig:pwr-fp-full-average}
shows the relative difference in fission product concentrations between OpenMC
and Serpent for this case. Most of the differences are less than 0.2\%, and only
a few fission products show differences up to 0.5\%.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_fp_full_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and interpolated FPYs.}
  \label{fig:pwr-fp-full-average}
\end{figure}

\Cref{fig:pwr-fp-full-thermal} shows the predicted fission product concentrations
when using the full depletion chain along with thermal FPYs. In this case,
although most fission products are within 1\% of Serpent, they are
systematically overpredicted other than a few nuclides. Because Serpent uses the
average fission energy to interpolate between two sets of FPYs, the systematic
difference is expected when using thermal FPYs in OpenMC. As the incident energy
of a neutron causing fission increases, the ``saddle'' and ``wings'' in the FPY
curve tend to increase significantly, and the peaks around $A=95$ and $A=135$
tend to slightly decrease. This corresponds to exactly what is observed in
\cref{fig:pwr-fp-full-thermal}. Because thermal FPYs were used in OpenMC for
this case, we expect that fission products near one of the two peaks of the FPY
curve will be slightly overpredicted relative to Serpent, and fission products
away from the peak will be underpredicted. This can be confirmed for particular
nuclides. Take, for example, $^{109}$Ag; in the $A=109$ mass chain, the nuclides
with the highest independent yields are $^{109}$Tc and $^{109}$Mo. Both these
nuclides have independent yields that increase significantly with increasing
neutron energy. The same situation occurs for $^{129}$I, whose predominant
precursor is $^{129}$Sn. The independent yields for these three precursor
nuclides are shown in \cref{tab:fp-yields}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_fp_full_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and thermal FPYs.}
  \label{fig:pwr-fp-full-thermal}
\end{figure}
\begin{table}[htbp]
  \centering
  \caption{Independent yields of select fission products due to fission in
  $^{235}$U (data from the ENDF/B-VII.1 FPY sublibrary).}
  \label{tab:fp-yields}
  \begin{tabular}{cccc}
    \toprule
    \textbf{Energy Spectrum} & \textbf{$^{109}$Tc} & \textbf{$^{109}$Mo} & \textbf{$^{129}$Sn} \\
    \midrule
    Thermal & 0.00013 & 0.00015 & 0.00230 \\
    Fast & 0.00034 & 0.00042 & 0.00550 \\
    Fusion & 0.00598 & 0.00109 & 0.01162 \\
    \bottomrule
  \end{tabular}
\end{table}

\Cref{fig:pwr-fp-casl-average} shows the relative difference in predicted
fission product concentrations between OpenMC and Serpent when using the CASL
depletion chain and interpolated FPYs. As in \cref{fig:pwr-fp-full-average},
almost all fission products are predicted to well within 1\% at 50 MWd/kg.
However, in this case there is one clear outlier: $^{85}$Kr. Upon further
investigation, it was determined that the root cause for this difference is the
fact that the CASL depletion chain uses a cumulative yield for $^{85}$Kr, and
the cumulative yield of $^{85}$Kr is known to be inconsistent with the
independent yields of the $A=85$ mass chain in
ENDF/B-VII.1~\citep{pigni2015nds}. Serpent relies solely on independent yields
in its depletion solver (as does the full depletion chain). We can conclude,
then, that there is nothing inherently wrong with the CASL depletion chain or
OpenMC; it is simply a matter of the underlying nuclear data being inconsistent.
The 5\% underprediction of $^{85}$Kr is also likely responsible for the slightly
higher difference in $k_\text{eff}$ for the CASL depletion chain shown in
\cref{fig:pwr-keff}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_fp_casl_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and interpolated FPYs.}
  \label{fig:pwr-fp-casl-average}
\end{figure}

\Cref{fig:pwr-fp-casl-thermal} shows the relative difference in predicted in
fission product concentrations when using the CASL depletion chain along with
thermal FPYs. The results are quite close to those shown
\cref{fig:pwr-fp-full-thermal}, with the exception of $^{85}$Kr for the
aforementioned reasons.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_fp_casl_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and thermal FPYs.}
  \label{fig:pwr-fp-casl-thermal}
\end{figure}

@@

\Cref{fig:sfr-actinides} shows the relative difference in predicted actinide
concentrations between OpenMC and Serpent with probability tables turned on. For
both the full and CASL depletion chains, the relative differences are all within
0.2\%. While this may seem close, the observed difference in $^{238}$U and
$^{239}$Pu concentrations merits special mention. In this model, the fuel
material is at \SI{807}{\kelvin}, but the endf71x library contains cross
sections processed at \SI{600}{\kelvin} and \SI{900}{\kelvin}. Thus, Serpent
ends up using probability tables at \SI{600}{\kelvin} rather than
\SI{807}{\kelvin}, which results in less parasitic absorption in $^{238}$U and
consequently less production of $^{239}$Pu (hence a lower $k_\text{eff}$ than
OpenMC with increasing burnup). Although OpenMC also does not have access to
probability tables at the exact fuel temperature, it statistically interpolates
between the probability tables at \SI{600}{\kelvin} and \SI{900}{\kelvin}.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_actinides_full.pdf}
    \caption{Full depletion chain}
    \label{fig:sfr-actinides-full}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_actinides_casl.pdf}
    \caption{CASL depletion chain}
    \label{fig:sfr-actinides-casl}
  \end{subfigure}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables on.}
  \label{fig:sfr-actinides}
\end{figure}

When probability tables are turned off, very close agreement is observed between
the predicted actinide concentrations in OpenMC and Serpent, as shown in
\cref{fig:sfr-actinides-nop}. In this case, the actinide concentrations agree to
within 0.01\% at all times during depletion for both the full and CASL depletion
chains.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_actinides_full_nop.pdf}
    \caption{Full depletion chain}
    \label{fig:sfr-actinides-full-nop}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_actinides_casl_nop.pdf}
    \caption{CASL depletion chain}
    \label{fig:sfr-actinides-casl-nop}
  \end{subfigure}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables off.}
  \label{fig:sfr-actinides-nop}
\end{figure}

\Cref{fig:sfr-fp} shows the relative difference in fission product
concentrations between OpenMC and Serpent with probability tables turned on.
Most differences between OpenMC and Serpent are below 1\%. As with the PWR
pincell model, OpenMC tends to produce a lower concentration of $^{109}$Ag most
likely because of differences in the treatment of FPY energy dependence. The
only noticeable difference between the full and CASL depletion chains is for
$^{85}$Kr, which is again explained by the use of an inconsistent cumulative
yield in the CASL depletion chain.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_fp_full_average.pdf}
    \caption{Full depletion chain}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_fp_casl_average.pdf}
    \caption{CASL depletion chain}
  \end{subfigure}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables on.}
  \label{fig:sfr-fp}
\end{figure}

With probability tables turned on, the differences between OpenMC and Serpent in
fission product concentrations are mostly the same as when probability tables
were turned off, as shown in \cref{fig:sfr-fp-nop}. Because the difference in
$^{238}$U and $^{239}$Pu concentrations was less than 0.2\% in
\cref{fig:sfr-actinides}, it makes sense that the use of probability tables
would not have a large effect on the fission product concentrations. Again, most
fission product concentrations agree to within 1\%, with $^{109}$Ag and
$^{85}$Kr being the notable outliers.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_fp_full_average_nop.pdf}
    \caption{Full depletion chain}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr/sfr_fp_casl_average_nop.pdf}
    \caption{CASL depletion chain}
  \end{subfigure}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables off.}
  \label{fig:sfr-fp-nop}
\end{figure}

>>>>

\Cref{fig:pwr-actinides-full} shows the relative difference in predicted
actinide concentrations between OpenMC and Serpent at four different burnup
values. The fission products that are shown in \cref{fig:pwr-actinides-full}
have been chosen because they are either strong neutron absorbers or significant
contributors to decay heat and/or radiotoxicity. We see that most of the
differences are less than 0.1\%, and all are within 0.15\%. The differences in
$^{235}$U and $^{239}$Pu concentrations increase slightly with increasing
burnup, which most likely accounts for the 20 pcm difference observed for the
full chain in \cref{fig:pwr-keff}. While not shown, the predicted actinide
concentrations for the reduced chain are nearly identical to those observed for
the full chain in \cref{fig:pwr-actinides-full}. \Cref{fig:pwr-actinides-casl}
shows the differences in actinide concentrations using the CASL depletion chain.
Because the CASL depletion chain differs from the full depletion chain primarily
with respect to how fission products are treated, the differences reported in
\cref{fig:pwr-actinides-casl} closely mirror those in
\cref{fig:pwr-actinides-full}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_actinides_full.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the full
  depletion chain.}
  \label{fig:pwr-actinides-full}
\end{figure}
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_actinides_casl.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the CASL
  depletion chain.}
  \label{fig:pwr-actinides-casl}
\end{figure}

The predicted concentration of fission products depends on both the depletion
chain that is used and the method for handling the energy dependence of the FPY.
We begin with results for the full depletion chain and interpolated FPYs, which
most closely matches the method used in Serpent; \cref{fig:pwr-fp-full-average}
shows the relative difference in fission product concentrations between OpenMC
and Serpent for this case. Most of the differences are less than 0.2\%, and only
a few fission products show differences up to 0.5\%.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_full_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and interpolated FPYs.}
  \label{fig:pwr-fp-full-average}
\end{figure}

\Cref{fig:pwr-fp-full-thermal} shows the predicted fission product concentrations
when using the full depletion chain along with thermal FPYs. In this case,
although most fission products are within 1\% of Serpent, they are
systematically overpredicted other than a few nuclides. Because Serpent uses the
average fission energy to interpolate between two sets of FPYs, the systematic
difference is expected when using thermal FPYs in OpenMC. As the incident energy
of a neutron causing fission increases, the ``saddle'' and ``wings'' in the FPY
curve tend to increase significantly, and the peaks around $A=95$ and $A=135$
tend to slightly decrease. This corresponds to exactly what is observed in
\cref{fig:pwr-fp-full-thermal}. Because thermal FPYs were used in OpenMC for
this case, we expect that fission products near one of the two peaks of the FPY
curve will be slightly overpredicted relative to Serpent, and fission products
away from the peak will be underpredicted. This can be confirmed for particular
nuclides. Take, for example, $^{109}$Ag; in the $A=109$ mass chain, the nuclides
with the highest independent yields are $^{109}$Tc and $^{109}$Mo. Both these
nuclides have independent yields that increase significantly with increasing
neutron energy. The same situation occurs for $^{129}$I, whose predominant
precursor is $^{129}$Sn. The independent yields for these three precursor
nuclides are shown in \cref{tab:fp-yields}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_full_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  full depletion chain and thermal FPYs.}
  \label{fig:pwr-fp-full-thermal}
\end{figure}
\begin{table}[htbp]
  \centering
  \caption{Independent yields of select fission products due to fission in
  $^{235}$U (data from the ENDF/B-VII.1 FPY sublibrary).}
  \label{tab:fp-yields}
  \begin{tabular}{cccc}
    \toprule
    \textbf{Energy Spectrum} & \textbf{$^{109}$Tc} & \textbf{$^{109}$Mo} & \textbf{$^{129}$Sn} \\
    \midrule
    Thermal & 0.00013 & 0.00015 & 0.00230 \\
    Fast & 0.00034 & 0.00042 & 0.00550 \\
    Fusion & 0.00598 & 0.00109 & 0.01162 \\
    \bottomrule
  \end{tabular}
\end{table}

\Cref{fig:pwr-fp-casl-average} shows the relative difference in predicted
fission product concentrations between OpenMC and Serpent when using the CASL
depletion chain and interpolated FPYs. As in \cref{fig:pwr-fp-full-average},
almost all fission products are predicted to well within 1\% at 50 MWd/kg.
However, in this case there is one clear outlier: $^{85}$Kr. Upon further
investigation, it was determined that the root cause for this difference is the
fact that the CASL depletion chain uses a cumulative yield for $^{85}$Kr, and
the cumulative yield of $^{85}$Kr is known to be inconsistent with the
independent yields of the $A=85$ mass chain in
ENDF/B-VII.1~\citep{pigni2015nds}. Serpent relies solely on independent yields
in its depletion solver (as does the full depletion chain). We can conclude,
then, that there is nothing inherently wrong with the CASL depletion chain or
OpenMC; it is simply a matter of the underlying nuclear data being inconsistent.
The 5\% underprediction of $^{85}$Kr is also likely responsible for the slightly
higher difference in $k_\text{eff}$ for the CASL depletion chain shown in
\cref{fig:pwr-keff}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_casl_average.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and interpolated FPYs.}
  \label{fig:pwr-fp-casl-average}
\end{figure}

\Cref{fig:pwr-fp-casl-thermal} shows the relative difference in predicted in
fission product concentrations when using the CASL depletion chain along with
thermal FPYs. The results are quite close to those shown
\cref{fig:pwr-fp-full-thermal}, with the exception of $^{85}$Kr for the
aforementioned reasons.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr_fp_casl_thermal.pdf}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the
  CASL depletion chain and thermal FPYs.}
  \label{fig:pwr-fp-casl-thermal}
\end{figure}

@@

\Cref{fig:sfr-actinides} shows the relative difference in predicted actinide
concentrations between OpenMC and Serpent with probability tables turned on. For
both the full and CASL depletion chains, the relative differences are all within
0.2\%. While this may seem close, the observed difference in $^{238}$U and
$^{239}$Pu concentrations merits special mention. In this model, the fuel
material is at \SI{807}{\kelvin}, but the endf71x library contains cross
sections processed at \SI{600}{\kelvin} and \SI{900}{\kelvin}. Thus, Serpent
ends up using probability tables at \SI{600}{\kelvin} rather than
\SI{807}{\kelvin}, which results in less parasitic absorption in $^{238}$U and
consequently less production of $^{239}$Pu (hence a lower $k_\text{eff}$ than
OpenMC with increasing burnup). Although OpenMC also does not have access to
probability tables at the exact fuel temperature, it statistically interpolates
between the probability tables at \SI{600}{\kelvin} and \SI{900}{\kelvin}.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_actinides_full.pdf}
    \caption{Full depletion chain}
    \label{fig:sfr-actinides-full}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_actinides_casl.pdf}
    \caption{CASL depletion chain}
    \label{fig:sfr-actinides-casl}
  \end{subfigure}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables on.}
  \label{fig:sfr-actinides}
\end{figure}

When probability tables are turned off, very close agreement is observed between
the predicted actinide concentrations in OpenMC and Serpent, as shown in
\cref{fig:sfr-actinides-nop}. In this case, the actinide concentrations agree to
within 0.01\% at all times during depletion for both the full and CASL depletion
chains.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_actinides_full_nop.pdf}
    \caption{Full depletion chain}
    \label{fig:sfr-actinides-full-nop}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_actinides_casl_nop.pdf}
    \caption{CASL depletion chain}
    \label{fig:sfr-actinides-casl-nop}
  \end{subfigure}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables off.}
  \label{fig:sfr-actinides-nop}
\end{figure}

\Cref{fig:sfr-fp} shows the relative difference in fission product
concentrations between OpenMC and Serpent with probability tables turned on.
Most differences between OpenMC and Serpent are below 1\%. As with the PWR
pincell model, OpenMC tends to produce a lower concentration of $^{109}$Ag most
likely because of differences in the treatment of FPY energy dependence. The
only noticeable difference between the full and CASL depletion chains is for
$^{85}$Kr, which is again explained by the use of an inconsistent cumulative
yield in the CASL depletion chain.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_fp_full_average.pdf}
    \caption{Full depletion chain}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_fp_casl_average.pdf}
    \caption{CASL depletion chain}
  \end{subfigure}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables on.}
  \label{fig:sfr-fp}
\end{figure}

With probability tables turned on, the differences between OpenMC and Serpent in
fission product concentrations are mostly the same as when probability tables
were turned off, as shown in \cref{fig:sfr-fp-nop}. Because the difference in
$^{238}$U and $^{239}$Pu concentrations was less than 0.2\% in
\cref{fig:sfr-actinides}, it makes sense that the use of probability tables
would not have a large effect on the fission product concentrations. Again, most
fission product concentrations agree to within 1\%, with $^{109}$Ag and
$^{85}$Kr being the notable outliers.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_fp_full_average_nop.pdf}
    \caption{Full depletion chain}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[t]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/sfr_fp_casl_average_nop.pdf}
    \caption{CASL depletion chain}
  \end{subfigure}
  \caption{Relative difference in fission product concentrations between OpenMC
  and Serpent for the SFR assembly model at 80, 180, 260, and 360 days with
  probability tables off.}
  \label{fig:sfr-fp-nop}
\end{figure}
